How to compute the fusion product of MV cycles in type A

### 2021-04-12 draft.tex
minor issue with ES rewrite

\begin{definition}
The nilpotent orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
\end{definition}  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
    % 
\begin{definition}
 For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
\end{definition}  
    % \acom{$s\in\AA$?}
    % 
     A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
    %

     Its closure is $ \overline{\OO}^{\lambda', \lambda''}_{0,s} = \bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.

     We recall that these adjoint orbit closures are given by rank conditions.  More precisely we have
     $$
     \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^i \le N - \#\text{~boxes in first $i$ columns of }\lambda \}
     $$
     and
     \begin{equation} \label{eq:ranks}
     \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i \le N - 
     \#\text{~boxes in first $i$ columns of }\lambda' \quad
     \rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
     \end{equation}

\begin{proposition} \label{prop:adjoint}
    There exists a flat family  $\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $s \in \AA$ is reduced and given by
       $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ if $s \ne 0 $ and
$        \overline{\OO}^\lambda $ if $ s = 0$.
\end{proposition}

In order to prove this result, we will need to recall some results from Eisenbud-Saltman \cite{eisenbud1989rank}.

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.}

Let $ W$ be a subspace of $ \AA^k$.  Eisenbud-Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.  We will now describe these fibres.

Let $ z \in \AA^k$. Some of the coordinates of $z$ are equal; we introduce some data to describe these equalities.  There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that $$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)} $$

\jcom{Eisenbud-Saltman don't introduce this $ s_j$ notation, but I find it helpful.}

Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
\begin{equation} \label{eq:ESfibre}
X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_j)^i\le r_{z,j}(i) \text{ for all } i , j \text{ as above}\}.
\end{equation}

@@

Define 
$$r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda$$
It is easy to see that this is a rank function, with $ k = \lambda_1$, the number of columns of $ \lambda$.
%\begin{lemma}
%   The function $r$
%    defined by $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ 
%is a rank function. 
%\end{lemma}

@@

For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1 \dots + k$.

For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduces the permutation $ p$, that $ r = 2 $, and that
\begin{equation} \label{eq:rcols}
r_{z(s), 1}(i) =  N - 
     \#\text{~boxes in first $i$ columns of }\lambda'
     \quad
     r_{z(s), 2}(i) =  N - \#\text{~boxes in first $i$ columns of }\lambda'' 
     \end{equation}
On the other hand, for $z(0)$, we get $ r = 1$ and that 
\begin{equation} \label{eq:rcol2}
r_{z(0),1}(i) = r(i) = n -  N - 
     \#\text{~boxes in first $i$ columns of }\lambda
\end{equation}
\jcom{Someone should check that I chose the notation correctly to make this work out.}

Let $ W = \{ z(s) : s \in \CC \}$.  Combining (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) we see that the Eisenbud-Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
\end{proof}

@@

\subsection{The Mirkovic-Vybornov slice} Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
\begin{definition}The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
\end{definition}
\jcom{I'm not a huge fan of this description, but I don't know how to write it better.}

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]
    \]
    % 
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example,
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]\,. 
    \]
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]
    % 
    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
    % \acom{Ok.}
    % 
    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    \end{definition}
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

@@

    Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.  By definition, $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.  This means that $t $ acting on 
    % $ \CC\xt^m / L(0)$ 
    $\cO^m/L(0)$ has Jordan type $ \lambda'$ and $ t$ acting on 
    % $ \CC\xt[t-s]^m / L(s) $ 
    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  For $ a = 0, s$,  we see that $$\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a). $$
    Thus, Lemma \ref{le:linalg} shows that the map
    % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
    $\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.   The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$. This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i). \acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
    % todo

@@

    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$. \rcom{Preimage of $\beta_\mu$}  This follows immediately from (iii).
    % 
\end{proof}
% \acom{note-to-self, skipped this; return to it.}
% 
\begin{lemma}
    Let $\mu',\mu'' \in P$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
\end{lemma}
%\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
% Resolved? the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too.. Anyway I think that you address this below Joel.

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
    Moreover,
    $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
    Note that 
    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t]) $.  Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $ \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}.  Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\CC\xt[t^{-1}])$, the result follows.
    \end{proof}

@@

The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
% 
\begin{theorem} \label{th:TmuWmu}
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{\CC[t]^m/L} ]^{tr}_{\beta_\mu} \,. $$
%\acom{Up to transpose?!}
\end{theorem}
%

For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ with $\cW_\mu$.  
As $  \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the composition
$$ 
\overline{\Gr}^{\lambda', \lambda''}_{0,\AA}  \hookrightarrow \Grbd \rightarrow \Grth\,.
$$
This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective.

In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $). \acom{Grammar of `write using the map' is iffy. Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}

\begin{theorem} \label{th:OGrl}
    There is an isomorphism
    $$\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
    given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
\end{theorem}
% \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
% \jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
% TODO: comb the doc at the end for this notation 
\begin{proof}
Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
This follows immediately from Lemma \ref{le:Grl1l2}.
\end{proof}

>>>>

\begin{definition}
The nilpotent orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
\end{definition}  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
    % 
\begin{definition}
    For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
\end{definition}  
A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
%

The closure $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ is $\bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.

We recall that these adjoint orbit closures are given by rank conditions.  More precisely we have
$$
    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^i \le N - \#\text{~boxes in first $i$ columns of }\lambda \}
$$
and
\begin{equation} 
\label{eq:ranks}
\begin{split}
    % 
    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : &\rk A^i \le N - 
    \#\text{~boxes in first $i$ columns of }\lambda' \\
    &\rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
\end{split}
\end{equation}
%  
\begin{proposition} \label{prop:adjoint}
    There exists a flat family  $\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $s \in \AA$ is reduced and given by
       $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ if $s \ne 0 $ and
$        \overline{\OO}^\lambda $ if $ s = 0$.
\end{proposition}
% 
In order to prove this result, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}.
%

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?}

Let $ W$ be a subspace of $ \AA^k$. Eisenbud \& Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions. We will now describe these fibres.

Let $ z \in \AA^k$. Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities. There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that 
$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,. $$

\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}

\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}

Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N - r(p(k_j)) + r(p(k_j + i)) \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}

% 
By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
\begin{equation} \label{eq:ESfibre}
X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_j)^i\le r_{z,j}(i) \text{ for all } i , j \text{ as above}\}.
\end{equation}

@@

Define 
$$r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,.$$
It is easy to see that this is a rank function, with $ k = \lambda_1$, the number of columns of $ \lambda$.
%\begin{lemma}
%   The function $r$
%    defined by $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ 
%is a rank function. 
%\end{lemma}

@@

For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.

For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduce the permutation $ p$, that $ r = 2 $, and that
\begin{equation} 
    \label{eq:rcols}
\begin{split}
        r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
        r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
\end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ r = 1$ and that 
\begin{equation} \label{eq:rcol2}
r_{z(0),1}(i) = r(i) = n -  N - 
     \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
\jcom{Someone should check that I chose the notation correctly to make this work out.}

\acom{What do we mean by equalities in $z(s)$ reproduce $p$? I thought $z(s)$ was defined by $p$. Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}. We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$. I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$.}

% 
Let $ W = \{ z(s) : s \in \CC \}$.  Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2} 
% (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) 
we see that the Eisenbud--Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
\end{proof}

@@

\subsection{The Mirkovic--Vybornov slice} 
% 
Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
\begin{definition}The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
\end{definition}
\jcom{I'm not a huge fan of this description, but I don't know how to write it better.}

\acom{Agree. Happy to just have the in-words description.}

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]\,. 
    \]
    % 
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example,
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]\,. 
    \]
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]
    % 
    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
    % \acom{Ok.}
    % 
    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
    $$
    \end{definition}
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

@@

    Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.  By definition, $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.  This means that $t $ acting on 
    % $ \CC\xt^m / L(0)$ 
    $\cO^m/L(0)$ has Jordan type $ \lambda'$ and $ t$ acting on 
    % $ \CC\xt[t-s]^m / L(s) $ 
    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  For $ a = 0, s$,  we see that $$\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a). $$
    Thus, Lemma \ref{le:linalg} shows that the map
    % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
    $\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.   The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$. This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i). 
    % \acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
    % todo

@@

    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.

    \rcom{Preimage of $\beta_\mu$}

    This follows immediately from (iii).
    % 
\end{proof}
% \acom{note-to-self, skipped this; return to it.}
% 
\begin{lemma}
    Let $\mu',\mu'' \in P$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
\end{lemma}
%\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
% Resolved? the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too.. Anyway I think that you address this below Joel.

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
    Moreover,
    $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
    Note that 
    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t]) $.  Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $. % \CC\xt[t^{-1}]s

    \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}

    \acom{Si}

    Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
    \end{proof}

@@

The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
% 
\begin{theorem} \label{th:TmuWmu}
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. $$
%\acom{Up to transpose?!}
\end{theorem}
%

For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ with $\cW_\mu$.  
As $  \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the composition
$$ 
\overline{\Gr}^{\lambda', \lambda''}_{0,\AA}  \hookrightarrow \Grbd \rightarrow \Grth\,.
$$
This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective. 
% Joel: The only non-injectivity comes from the fact that we forget the data
% of s.  So the map is non-injective over the locus where s is not
% actually an eigenvalue (in lattice terms where L(s) is the standard
% lattice).
In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $). 
% \acom{Grammar of `write using the map' is iffy. Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}

\begin{theorem} \label{th:OGrl}
    There is an isomorphism
    $$\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
    given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
\end{theorem}
% \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
% \jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
% TODO: comb the doc at the end for this notation 
\begin{proof}
Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, 
$$ 
(A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu \,. 
$$
This follows immediately from Lemma \ref{le:Grl1l2}.
\end{proof}
% 
\begin{theorem}
    The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
    $$ 
    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \UU^{\mu', \mu''}_{0,\AA} \cong \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} \cap S^{\mu', \mu''}_{0,\AA}\,.
    $$
\end{theorem}
